Title Goes Here

### 2020-04-10 analysis/paper/paper.Rmd
prepare homework

SAA18 <- readxl::read_excel(here("analysis/data/2018 SAA Title.xlsx"))
EAA18 <- readxl::read_excel(here("analysis/data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/2018 CAA.xlsx"))

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
# my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

>>>>

SAA18 <- readxl::read_excel(here("analysis/data/raw-data/2018 SAA Title.xlsx"))
EAA18 <- readxl::read_excel(here("analysis/data/raw-data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/raw-data/2018 CAA.xlsx"))

@@

```{r}
# make the custom functions available here in this Rmd file
source(here::here("analysis/paper/functions-for-gender.R"))
source(here::here("analysis/paper/functions-for-topic-models.R"))
```

```{r}
# let's run the topic model fn for each conf
CAA18_tm <- do_the_topic_model(CAA18)
xxx_tm <- do_the_topic_model(xxx)
xxx_tm <- do_the_topic_model(xxx)

# Let's save the output for each one
saveRDS(CAA18_tm, here::here("analysis/data/derived-data/CAA18_topic_model.rds"))
saveRDS(xxx_tm, here::here("analysis/data/derived-data/xxx_topic_model.rds"))
saveRDS(xxx_tm, here::here("analysis/data/derived-data/xxx_topic_model.rds"))
```
